Token-level author diarization using clustering of stylistic contexts

### 2017-06-02 paper/paper.tex
no comment

don't forget to describe tolerance

@@

hard task, a lot of space for improvement

@@

We have presented some ideas that are not completely refined but, based on the data we have available, seem to give comparable, or even better results that the other two approaches that tired to tackle the same problem.

 and that there is a lot of room for improvement for our approach

 as well as in exploring other

>>>>

@@

@@

We have presented some ideas that are not completely explored but, based on the data we have available, seem to give comparable, or even better results than the other two approaches that tired to tackle the same problem. There is a lot of room for improvement of our approach, as well as in exploring other new ideas.

For further work, we could include more basic features, try other clustering  algorithms and use more systematic approach for choosing (unknown) hyperparameters. Our transformation could be tested on other authorship analysis tasks.
